Learning filters from user provided image makers

### 2020-06-03 main.tex
definition of adjacency

\section{Learning filters from markers}
Our method is based on the idea that the network designer is an expert in the application domain or knows well enough to indicate which are the relevant characteristics of the objects of interest. The designer highlights these regions by placing markers. For each marker, the extended local feature vectors of its spels are taken. These vectors are clustered and the centers of those groups are used as filters for the current convolutional layer. Since each convolutional layer transforms the input feaure space of the images into a new one, the same procedure can be repeated to create the filters of the subsequents convolutional layers. This way, it is enough to specify the number of desired convolutional layers and their hyperparameters.

Let $\D$ be a dataset of images. The designer draws markers on only a subset of the images, let's say $\pDD \subseteq \D$. That is, she produces for each $\I \in \pDD$ a set of markers $\M(\I)$.  This subset of images, using the information from the markers, is used to create a set of patches \[\Pa(\pDD) = \bigcup_{\I \in \pDD}{P(\I, \M, \A)},\] with respect to an adjacency relation also defined by the designer. In this work, we use only circular adjacency relations.

>>>>

\section{Learning filters from markers}
Our method is based on the idea that the network designer is an expert in the application domain or knows well enough to indicate which are the relevant characteristics of the objects of interest. The designer highlights these regions by placing markers, which are associate to pixels. For each marker, we create a extended feature vector by taken the pixel's feature vector and of its neiborhs. These vectors are clustered and the centers of those groups are used as filters for the current convolutional layer. Since each convolutional layer transforms the input feaure space of the images into a new one, the same procedure can be repeated to create the filters of the subsequents convolutional layers. This way, it is enough to specify the number of desired convolutional layers and their hyperparameters.

Let $\D$ be a dataset of images. For an image $I \in \D$, the adjacency $\A$ of a pixel $p = (x, y)$ of $I$ is a set pixels $\A(p) = \{ p_1, p_2, \ldots, p_n \}$. In this work, we only consider a paritcular case of adjacency, 
\[\A_k(p) = \{(x^\prime, y^\prime) :\, \sqrt{(x - x^\prime)^2 + (y - y^\prime)^2} \le k\}.\]
The designer draws markers on only a subset of the images, let's say $\pDD \subseteq \D$. That is, she produces for each $I \in \pDD$ a set of markers $\M(I)$.  This subset of images, using the information from the markers, is used to create a set of patches \[\Pa(\pDD) = \bigcup_{\I \in \pDD}{P(\I, \M, \A)},\] with respect to an adjacency relation also defined by the designer. In this work, we use only circular adjacency relations.
